---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chkchk

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of {chkchk} is to determine if load-time elision is a suitable way to improve the runtime performance of packages that use assertions to check validity of their arguments.

## Installation

You can install the released version of chkchk from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("chkchk")
```

## Example

{chkchk} behaves differently depending on whether the package is loaded from an installation or using `pkgload::load_all()`.

### Installed

```{r installed, error = TRUE}
library(chkchk)

# Both arguments must be `TRUE`...
chkchk(FALSE, FALSE)

# ...but this isn't enforced when the package is installed.
chkchk(TRUE, FALSE)
chkchk(TRUE, TRUE)

# Source code for the internal function that has checks for the second argument
# which are elided on load time:
chkchk:::internal
```


### Loaded

```{r loaded, error = TRUE}
pkgload::load_all()

# When loaded, the check on the second argument is enforced too.
chkchk(TRUE, FALSE)
chkchk(TRUE, TRUE)

# True source code for the internal function:
chkchk:::internal
```
